Finance and Income Inequality - panel BMA approach\thanks{We thank two anonymous referees, ...}

### 2019-12-30 Paper/paper.tex
update literature

\acrodef{bma}[BMA]{Bayesian Model Averaging}
\acrodef{bic}[BIC]{Bayesian Information Criterion}
\acrodef{cbf}[CBF]{Conditional Bayes Factor}
\acrodefplural{cbf}[CBFs]{Conditional Bayes Factors}
\acrodef{cswd}[CSWD]{Credit Suisse Wealth Databook}
\acrodef{gfdd}[GFDD]{Global Financial Development Database}
\acrodef{pip}[PIP]{Posterior Inclusion Probability}
\acrodefplural{pip}[PIPs]{Posterior Inclusion Probabilities}
\acrodef{fdi}[FDI]{Foreign Direct Investment}
\acrodefplural{fdi}[FDIs]{Foreign Direct Investments}
\acrodef{gdp}[GDP]{Gross Domestic Product}
\acrodef{uip}[UIP]{Unit Information Prior}
\acrodef{wb}[WB]{World Bank}
\acrodef{oecd}[OECD]{Organisation for Co-operation and Development}
\acrodef{ivbma}[IVBMA]{Instrumental Variable Bayesian Model Averaging}
\acrodef{wid}[WID]{World Inequality Database}
\acrodef{hbs}[HBS]{Household Balance Sheet}
\acrodef{uk}[UK]{United Kingdom}
\acrodef{us}[US]{United States}
\acrodef{efw}[EFW]{Economic Freedom of the World}
\acrodef{pmp}[PMP]{Posterior Model Probability}

@@

@@

\citet{perottivolpin2004} present a theoretical framework how established interests lobby for lower investor protection to prevent entrance of the new competitors. Greater accountability of the politicians is reflected in higher bribe required from teh lobbyist therefore higher accountability implies higher market entry on more competition. After confirming their prediction empirically, they show that the most important factor of accountability is not the formal measure of democratic institutions, but \emph{newspaper readership} which they interpret as broad awareness of policy choices and their outcomes.

>>>>

\acrodef{bma}[BMA]{Bayesian Model Averaging}
\acrodef{bic}[BIC]{Bayesian Information Criterion}
\acrodef{cbf}[CBF]{Conditional Bayes Factor}
\acrodefplural{cbf}[CBFs]{Conditional Bayes Factors}
\acrodef{cswd}[CSWD]{Credit Suisse Wealth Databook}
\acrodef{gfdd}[GFDD]{Global Financial Development Database}
\acrodef{pip}[PIP]{Posterior Inclusion Probability}
\acrodefplural{pip}[PIPs]{Posterior Inclusion Probabilities}
\acrodef{fdi}[FDI]{Foreign Direct Investment}
\acrodefplural{fdi}[FDIs]{Foreign Direct Investments}
\acrodef{gdp}[GDP]{Gross Domestic Product}
\acrodef{uip}[UIP]{Unit Information Prior}
\acrodef{wb}[WB]{World Bank}
\acrodef{oecd}[OECD]{Organisation for Co-operation and Development}
\acrodef{ivbma}[IVBMA]{Instrumental Variable Bayesian Model Averaging}
\acrodef{wid}[WID]{World Inequality Database}
\acrodef{hbs}[HBS]{Household Balance Sheet}
\acrodef{uk}[UK]{United Kingdom}
\acrodef{us}[US]{United States}
\acrodef{efw}[EFW]{Economic Freedom of the World}
\acrodef{pmp}[PMP]{Posterior Model Probability}
\acrodef{wals}[WALS]{Weighted-average Least Squares}

@@

\citet{nolan2019drivers} bring a survey of the literature on determinants of inequality, summarizing the complexity of the inequality dynamics. They stress that many of the determinants are interlinked which implies difficulty in assigning precise effects to individual drivers of inequality. Additionally, they encourage complementary individual country case studies to support the finding of the general cross-country estimates.

@@

\citet{perotti2007investor} present a theoretical framework how established interests lobby for lower investor protection to prevent entrance of the new competitors. Greater accountability of the politicians is reflected in higher bribe required from teh lobbyist therefore higher accountability implies higher market entry on more competition. After confirming their prediction empirically, they show that the most important factor of accountability is not the formal measure of democratic institutions, but \emph{newspaper readership} which they interpret as broad awareness of policy choices and their outcomes.

Summary of the theoretical preditions in \citet{demirgucc2009finance} on pages 20-23 for the review.

\citet{furceri2019robust} apply \ac{wals} to identify robust determinants of income inequality. They are the closest paper to ours since they account for model uncertainty in the estimation. Their focus if more general rathar than on finance specifically. Out work offers more detailed contribution in terms of the role of finance in shaping income inequality. On the top of that, we differ from their analysis by examining multiple measures of inequality and specifically identifying the determinants of top income shares along with the determinants of the overall income distribution represented by income Gini index. We provide further evidence in all these dimensions.
